\documentclass[11]{article}

\begin{document}

\title{Intro to \LaTeX\ and me} 
\author{Chirag Sachdev}
\date{Week 1}
\maketitle

\begin{abstract}
  The purpose of this report is to demonstrate my skills in writing reports with \LaTeX . The skills included are the basics required for writing reports such as adding titles, sections, lists, date and acknowledgments.This report provides an insight to me, my background and why i chose the program.
\end{abstract}

\textbf{Acknowledgements}: I would like to thank Professor Shiu-Kai Chin foor giving tutorials on \LaTeX\ programming.

\section{Executive Summary}
\begin{description}

\item \textbf{All requirements of this project are met.}

\item \textbf{This report contains the following sections:}
\begin{enumerate}
	\item Executive Summary
	\item Where I grew up
	\item My program of study
	\item Why I picked my program of study
	\item Why I am taking Assurance Fundamentals
	\item What I hope to learn from Assurance Fundamentals
\end{enumerate}

\item \textbf{This document: } 
\begin{itemize}
	\item has been compiled with no errors for reproducability.
	\item includes the following data structures:
	\begin{enumerate}
		\item Numbered List
		\item Bulleted List
		\item Descriptive List
	\end{enumerate}
\end{itemize}
\end{description}

\newpage
\section{Where I grew up}
I grew up in Mumbai, India. The thing that I love most about Mumbai is that it is the city that never sleeps. Having spent 22 years of my life in Mumbai, theres no place quite like it. The best and the worst time to be in Mumbai is during the monsoon. Having the local street food served hot while sipping piping hot tea standing under an umbrella is an experience one should not miss. Along with the vastcostline contributing to many beaches, Mumbai is known for the food and the night-life.
Mumbai is the financial capital of India and falls in the region of tropical climate. The harshest winter I have seen in Mumbai was when the temperature got to 55 Farhenheit. 
Mumbai is the city of dreams and I can't wait to visit it again.


\section{My program of study}
I am pursuing a Master's Degree in Cybersecurity with an inclination towards Machine Learning. The program at Syracuse University is perfectly tailored with highly recognized and influential faculty to support the students through their education.
I began my course at Drexel where i studied the following subjects:



\section{Why I picked my program of study}
The first time I encountered an incident in this domain and its many perils was when one of
my social networking accounts was compromised and the attacker masquerading as me,
sent out messages to my contacts asking for my personal details. I was notified of this
activity immediately and managed to recover my account credentials with the limited
knowledge I possessed at that time. This incident sparked a fire of curiosity inside me for the
importance of security in this aspect of life. I then went ahead to increase my awareness by
getting certified as a Certified Ethical Hacker(CISEH). This was a pathway to my
concentration on cyber security as it taught me the basic procedures and methods followed
by ethical hackers to find out the diverse methods of compromising a system. I then
completed an advanced course as a Certified Penetration Testing Expert (CPTE), which is
built on firmly proven testing procedures that are capable of discovering the latest
vulnerabilities in a system. Using my newfound knowledge, I performed an analysis of my
college website and successfully found the bugs associated with it and was awarded a
certificate of appreciation from the Principal and Head of Computer Engineering.
I believed that my newfound skills were sufficient and I decided to put it to test. I realized that having applied knowledge is not sufficient in a dynamic world. In order to excel in my field I needed to revisit my foundations and hence decided to pursue a Master's degree in Cybersecurity to achieve the same.

\section{Why I am taking Assurance Foundations}
This course is taught by Professor Shiu-Kai Chin, a well establish computer scientist. It is an honour to be guided by him for this course. Assurance foundation is one of the course courses for my program.


\section{What do I expect to Learn from Assurance Foundations}
I hope to learn Access control logic and its principles along with functional programming from the course.
I believe that I would also be able to use theorem provers like HOL.

\end{document}
